### 2015-12-29 fundamentals/impl.tex
figure and table adjustments for final submission
reduces length of qa section at request of reviewer 2

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/framework}
\caption{The \Cyclus core provides \glspl{API} that abstract away the details in
the kernel and allow the archetypes to be loaded into the simulation in a modular
fashion.}
\end{center}
\label{fig:framework}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/modifiedopen.eps}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations\cite{carlsen_cyclus_2014}.}
\end{center}
\label{fig:modifiedopen}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/agent_uml}
\end{center}
\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[width=\columnwidth]{./images/compositions}
\end{center}
\caption{
A simple decay line cache holding compositions A, B, C, and a
yet-uncomputed composition D.  B comes from decaying A 1 time step.  C comes
from decaying B 2 time steps, etc.  Black represents the cache for this
particular composition chain. Blue indicates decay operations that can be
satisfied by cache lookups.   If A needs to be decayed 1 time step (A +1), a
quick lookup returns the previously computed B.  Decaying B 3 time steps
requires a decay calculation to compute a new composition D, but subsequent
requests such as decaying A 4 time steps will not require any recalculation.
}
\label{fig:compositions}
\end{figure}

@@

\begin{table*}[H]
\centering
\begin{tabularx}{\textwidth}{|r|l|X|}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. It requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$.}
\label{tab:cycamore}
\end{table*}

@@

Automated software \emph{testing} is the first line of defense against
errors in implementation. It also acts as an early warning sign if the
simulator does not work as intended on a new system.
Testing serves a critical role in \gls{QA} because it directly compares the
results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration
tests, and regression tests.  It is important to note that before a proposed
code change is allowed into \Cyclus,  the change must be covered by a test, either new or existing, and all tests must pass.

@@

Unit tests compare the results of the smallest code \emph{unit}, typically a
single function or a class.  \Cyclus uses the Google Test framework
\cite{inc_googletest_2008} as a harness for running unit tests. Sufficient unit
tests are required for any proposed change to the \Cyclus code base. Currently,
\Cyclus implements over 450 unit tests and \Cycamore implements 85.  These
cover approximately 65\% of their respective code bases, and these numbers are
expected to grow over time.

@@

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other. 
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations for scenarios that are sufficiently simple to predict the results
and verifying that results match those predictions. A set of standard input
files are run, then the output is inspected and compared via Nose
\cite{pellerin_nose_2007}, a Python test framework.  In this way, \Cyclus code
units are tested in the full context that they will be
executed. This category of testing is especially useful for ensuring that
major \Cyclus components are functioning as expected.

@@

\Gls{CI} is the idea that software should be tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  Under \gls{CI}, every pull request is automatically
tested independently, immediately as it is proposed. The results of this
testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
Whenever a pull request is created, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the
problems.

Since these steps are performed for all incoming code, it is easy for the
\Cyclus core team to determine whether or not an individual pull request
actually works. This helps identify build and test problems prior to broken
code being allowed into the main software development branch.

@@

Once \gls{CI} is successful, a code reviewer inspects not only the
changes that are proposed to the software itself, but also the changes that
have been proposed to tests.  It is important that the subset of tests that
are relevant to the software change has a scope and completeness that will
ensure that incorrect behavior will be automatically detected.  If there are
sufficent tests and \gls{CI} is successful, the reviewer can proceed to
considering the actual software changes themselves.

Because of their role in facilitating code review during the change process,
as well as their long term benefit to the maintainability of the project,
documentation and coding style are also reviewed as part of this process.

\paragraph{Documentation}

All of the public interface (the \gls{API}) must be documented as required by
the \Cyclus \gls{QA} policy. This certifies that the intended goals of an
\gls{API} are communicated explicitly by the author in prose form.  In \Cyclus,
this information is aggregated together into static websites with the Doxygen
\cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} tools, and
can be accessed at \url{http://fuelcycle.org}.

\paragraph{Style Guide}

In any multi-person software project, there is a tension between how individuals
wish to write code. Every person tends to have their own custom style. To remedy this,
coding style guides are the software analogy to those for written language,
such as the Chicago Manual of Style. \Cyclus strictly enforces the use of the
Google C++ Style Guide \cite{weinberger_google_2008} for all software contributions.
This means that all developers of \Cyclus nominally write \Cyclus code in the same
way.  This homogenization may be a hurdle to new developers but ultimately
improves code legibility and, therefore, robustness \cite{cohen_modern_2010}.

>>>>

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\columnwidth]{./images/framework}
\caption{The \Cyclus core provides \glspl{API} that abstract away the details in
the kernel and allow the archetypes to be loaded into the simulation in a modular
fashion.}
\end{center}
\label{fig:framework}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.8\columnwidth]{./images/modifiedopen.eps}
\caption{The \Cyclus framework enables fully open, partially open, and fully
closed collaborations\cite{carlsen_cyclus_2014}.}
\end{center}
\label{fig:modifiedopen}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\columnwidth]{./images/agent_uml}
\end{center}
\caption{Inheriting \Cyclus class interfaces, such as the \Class{Agent},
\Class{Facility}, \Class{Institution}, and \Class{Region} classes, abstracts away
unnecessary details while exposing powerful functionality. In the above
example, the \Class{Dummy} archetype simply inherits from \Class{Region} in
order to become a bona fide Region-type \Class{Agent}.}
\label{fig:agent_uml}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=\columnwidth]{./images/compositions}
\end{center}
\caption{
A simple decay line cache holding compositions A, B, C, and a
yet-uncomputed composition D.  B comes from decaying A 1 time step.  C comes
from decaying B 2 time steps, etc.  Black represents the cache for this
particular composition chain. Blue indicates decay operations that can be
satisfied by cache lookups.   If A needs to be decayed 1 time step (A +1), a
quick lookup returns the previously computed B.  Decaying B 3 time steps
requires a decay calculation to compute a new composition D, but subsequent
requests such as decaying A 4 time steps will not require any recalculation.
}
\label{fig:compositions}
\end{figure}

@@

\begin{table*}[htb]
\centering
\begin{tabularx}{\textwidth}{rlX}
\hline
\textbf{Entity} & \textbf{Archetype} & \textbf{Functionality} \\
\hline
Facility & EnrichmentFacility & This facility enriches uranium at a specified capacity. \\
Facility & Fab$^*$ & This facility fabricates fuel material based on separated streams. \\
Facility & Reactor$^*$ & A reactor model that handles batch refueling, based on pre-determined recipes of compositions. It requests any number of input fuel types and transmutes them to static compositions upon discharge.\\
Facility & Separations$^*$ & This facility separates an incoming material into specified streams. \\
Facility & Sink & This facility is capable of accepting a finite or infinite quantity of some commodity produced in the simulation. \\
Facility & Source & This facility generates material of the composition and commodity type specified as input.  \\
Institution & ManagerInst & The manager institution manages production of commodities among its facilities by building new ones as needed. \\
Institution & DeployInst &  This institution deploys specific facilities as defined explicitly in the input file. \\
Region & GrowthRegion & This region determines whether there is a need to meet a certain capacity (as defined via input) at each time step. \\
\hline
\end{tabularx}
\caption{The Archetypes in \Cycamore seek to cover a large range of simple
simulation use cases \cite{carlsen_cycamore_2014}. Facilities added in version
1.3 are marked with $^*$.}
\label{tab:cycamore}
\end{table*}

@@

Automated software \emph{testing} is the first line of defense against
errors in implementation. Testing directly compares the
actual results of running software versus the expected behavior of the software.
In \Cyclus, three categories of tests are defined: unit tests, integration
tests, and regression tests.  Before a proposed code change is allowed into 
\Cyclus,  the change must be covered by a test, either new or existing, and all 
tests must pass.

@@

Unit tests verify behavior of the smallest code \emph{unit}, typically a
single function or a class.  \Cyclus uses the Google Test framework
\cite{inc_googletest_2008} as a harness for running unit tests. Sufficient unit
tests are required for any proposed change to the \Cyclus code base. Currently,
\Cyclus implements over 450 unit tests and \Cycamore implements 85.  These
cover approximately 65\% of their respective code bases, and these numbers are
expected to grow over time.

@@

Integration tests combine multiple elements of the
\Cyclus interface and test that they work correctly with each other. 
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations for scenarios verifying that results match predictions. A set of standard input
files are run, then the output is inspected and compared via Nose
\cite{pellerin_nose_2007}, a Python test framework.

@@

\Gls{CI} is the idea that software should be automatically tested
and validated as it is being developed, rather than as a final stage in a
longer development cycle.  The results of this
testing are shown to code reviewers prior to reviewing the software changes themselves.  The \Cyclus
project currently uses the CircleCI \cite{biggar_circleci_2015} service for continuous integration.
When a code change is submitted for review, CircleCI builds a version of the \Cyclus
source code that includes the requested changes and runs the complete test
suite, reporting back whether or not those steps were successful. If \gls{CI}
was not successful, the code author(s) must first identify and resolve the 
problems.  These steps are performed for all incoming code prior to inclusion, 
so broken code never enters the main software development branch.

@@

Once \gls{CI} is successful, a code reviewer inspects not only the changes that 
are proposed to the software itself, but also the changes that have been 
proposed to tests.

Because of their long term benefit to the maintainability of the project, 
documentation and coding style are also reviewed as part of this process.  The 
\gls{API} must be documented as required by the \Cyclus \gls{QA} policy.  In 
\Cyclus, this information is aggregated together into static websites with the 
Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} 
tools, and can be accessed at \url{http://fuelcycle.org}. \Cyclus also strictly 
enforces the use of the Google C++ Style Guide \cite{weinberger_google_2008} 
for all software contributions.  This means that all developers of \Cyclus 
write \Cyclus code in the same way.  This homogenization may be a hurdle to new 
developers but ultimately improves code legibility and, therefore, robustness 
\cite{cohen_modern_2010}.
